---
title: "CS5801 Coursework Template Proforma"
author: "student-id"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_notebook
version: 1.0
---

# 0. Instructions 

*1. Remove the (italicised) guidance text but keep the section headings.*  
*2. Add as many chunks of R code as required.*  
*3. Summarise your answer to each section at the top of the section then add descriptions of your analysis plans and explanations of your code and findings.  Please be detailed and where you have made choices explain the rationale for them.*  
*4. Write your report using RMarkdown.  For guidance see a [helpful blog](https://www.dataquest.io/blog/r-markdown-guide-cheatsheet/#tve-jump-17333da0719) or use the R Markdown cheatsheet which can be accessed from within RStudio by selecting `Help > Cheatsheets > R Markdown Cheat Sheet`.*  
*5. Your report should be clearly and professionally presented with appropriate use of cited external sources. (5 marks)*  
*6. It should also be easy to understand, with well-documented code following the principles of literate programming. (5 marks)*  

```{r}
# Add code here to load any required libraries with `library()`.  
# We suggest you use `install.package()` for any required packages externally to this document 
# since installation only need be done once.
```


# 1. Organise and clean the data

## 1.1 Subset the data into the specific dataset allocated
 
*A description of the data set provided, its contents and which subset you should select is documented in the assessment brief at CS5801-Assessment Brief Template 2022-23.pdf*  
*Use R code to correctly select the subset of data allocated. (5 marks)*  

```{r}
# Assign your student id into the variable SID, for example:
SID <- 2101234                  # This is an example, replace 2101234 with your actual ID
SIDoffset <- (SID %% 100) + 1    # Your SID mod 100 + 1

load("house-analysis.RDa")
# Now subset the housing data set
# Pick every 100th observation starting from your offset
# Put into your data frame named mydf (you can rename it)
mydf <- house.analysis[seq(from=SIDoffset,to=nrow(house.analysis),by=100),]
```


## 1.2 Data quality analysis
 
*Provide a description of a comprehensive plan to assess the quality of the data, and document your findings.  Include all variables/columns (5 marks) from the data set and provide a full implementation (5 marks).  NB even if no data quality issues are identified you should still check and report.*

 
## 1.3 Data cleaning  
 
*List and explain the data quality issues found in 1.2 (5 marks), justify and document the responses made (if any) (5 marks).*


# 2. Exploratory Data Analysis (EDA)

## 2.1 EDA plan

*Outline a suitable plan to explore, describe and visualise your data. (5 marks)*  


## 2.2 EDA and summary of results  

*Undertake and summarise the findings of your data exploration, particularly with respect to the research questions.  Use appropriate summary statistics (uni- and multi-variate) and visualisations. Provide a concise summary of your findings at the top of this section (10 marks)*


## 2.3 Additional insights and issues

*Highlight potential further issues or insights uncovered in 2.2.  This might include follow up to findings from your initial EDA.  We accept that the boundary between 2.2 and 2.3 is somewhat arbitrary so use your judgement and maximise good structure and readability. (5 marks)*


# 3. Modelling

## 3.1 Explain your analysis plan

*Given the research question (i.e., property price) outline an analysis plan that incorporates/references any findings from the data cleaning (1.3) and EDA (2.2)  (5 marks). *

## 3.2 Build a model for property price
*Use R to build a suitable model (5 marks).*  
*NB Submissions where suitable models do not have good fit due to the nature of the data will not be penalised.*  


## 3.3 Critique model using relevant diagnostics

*Offer an interpretation of the model characteristics, goodness of fit and graphical diagnostics (5 marks) for the model built in 3.2. Explain any potential weaknesses (5 marks).*


## 3.4 Suggest improvements to your model

*Based on the findings in 3.2 and 3.3 articulates possible alternative approaches to address them (5 marks).*


# 4. Extension work

## 4.1 Model the likelihood of a property being furnished (using the is_furnished variable provided).

*Given this second research question (i.e., involving the binary target attribute) provide a plan of analysis based on relevant EDA for this attribute (10 marks). The model is described, explained and critiqued (10 marks).*
*NB Submissions where suitable models do not have good fit due to the nature of the data will not be penalised.* 

# References  

*Add any references here. NB You can either do this manually or automatically with a `.bib` file (which then must be submitted along with your `.Rmd` file).  See the RMarkdown [documentation](https://bookdown.org/yihui/rmarkdown-cookbook/bibliography.html) for guidance.*    